---
title: "Markov Chain Monte Carlo Visualization Functions"
author: "Michael Betancourt"
date: "May 2024"
toc: true
number-sections: true
highlight: pygments
crossref:
  lst-title: "Stan Program"
filters:
   - include-code-files
format:
  html:
    html-math-method: katex
    theme:
      - lux
      - custom.scss
    standalone: true
    embed-resources: true
    code-overflow: wrap
    linkcolor: "#B97C7C"
  pdf:
    keep-tex: true
    fig-width: 5.5
    fig-height: 5.5
    code-overflow: wrap
    monofontoptions:
      - Scale=0.5
knitr:
  opts_chunk:
    comment: ''
  opts_knit:
    global.par: TRUE
format-links: false
---

In this note I will review a suite of `R` functions that implement various
visualizations of probabilistic behavior using the output of a Markov chain
Monte Carlo algorithm.

Most of these visualizations utilize nested quantile intervals to visualize
one-dimensional pushforward behavior as described in
[Chapter 7, Section 5](https://betanalpha.github.io/assets/chapters_html/transforming_probability_spaces.html#sec:1d-pushforward-characterizations)
of my probability theory material.  The individual quantiles are consistently
estimated as the empirical average of the empirical quantiles derived from
individual Markov chains.  Because they do not communicate the quantile
estimator errors these visualizations can be misleading if the Markov chains do
not contain enough information.

# Initial Setup

First and foremost we have to set up our local `R` environment.

```{r}
#| echo: !expr knitr::is_html_output()
#| eval: !expr knitr::is_html_output()
par(family="sans", las=1, bty="l",
    cex.axis=1, cex.lab=1, cex.main=1,
    xaxs="i", yaxs="i", mar = c(5, 5, 3, 1))
  
```

```{r}
#| echo: !expr knitr::is_latex_output()
#| eval: !expr knitr::is_latex_output()
par(family="serif", las=1, bty="l", cex.axis=1, cex.lab=1, cex.main=1,
    xaxs="i", yaxs="i", mar = c(5, 5, 3, 5))
```

This includes loading up `RStan`.

```{r}
#| warning: false
#| message: false

library(rstan)
rstan_options(auto_write = TRUE)            # Cache compiled Stan programs
options(mc.cores = parallel::detectCores()) # Parallelize chains
parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
```

Finally we'll load my recommended
[Markov chain Monte Carlo analysis tools](https://github.com/betanalpha/mcmc_diagnostics)
and the visualization functions themselves.

```{r}
util <- new.env()
source('mcmc_analysis_tools_rstan.R', local=util)
```

```{r}
source('mcmc_visualization_tools.R', local=util)
```

# One-Dimensional Baseline Function

Our first example is one-dimensional curve-fitting, i.e. regression, model with
a linear baseline function,
$$
p(y_{n} \mid x_{n}, \alpha, \beta, \sigma)
=
\text{normal}(y_{n} \mid \alpha + \beta \, x_{n}, \sigma).
$$

## Data Exploration

What is data if not an opportunity to explore?

```{r}
data <- read_rdump("data/uni_data.R")
```

The `plot_line_hist` function constructs a histogram but then plots only its
outline, without lines separating the interior histogram bins.  Here we can
plot histograms summarizing the observed inputs
$$
\{ \tilde{x}_{1}, \ldots, \tilde{x}_{n}, \ldots, \tilde{x}_{N} \}
$$
and the observed outputs,
$$
\{ \tilde{y}_{1}, \ldots, \tilde{y}_{n}, \ldots, \tilde{y}_{N} \}.
$$

```{r}
par(mfrow=c(1, 2))

util$plot_line_hist(data$x, -6, 6, 0.5,
                    xlab="x", main="Observed Inputs")

util$plot_line_hist(data$y, -4, 7, 0.5,
                    xlab="y", main="Observed Outputs")
```

This presentation is a bit cleaner than conventional histogram plots, especially
when there is no ambiguity about the binning.

We can also plot histograms with arbitrary bin configurations.

```{r}
par(mfrow=c(1, 2))

util$plot_line_hist(data$x,
                    breaks=c(-6, -3, -1.5, -0.75, 0, 0.75, 1.5, 3, 6),
                    xlab="x", main="Observed Inputs")

util$plot_line_hist(data$y,
                    breaks=c(-4, 0, 7),
                    xlab="y", main="Observed Outputs")
```

A key advantage of reducing a histogram to its outline is that it is much easier
to overlay multiple histograms on top of each other without compromising
legibility.  The `plot_line_hists` function constructs and then overlays two
histograms with the same binning.

```{r}
par(mfrow=c(1, 1))

util$plot_line_hists(data$x, data$y, -6, 7, 0.5, xlab="")
text(-3.5, 90, cex=1.25, label="Observed\nInputs",
     pos=4, col="black")
text(3.5, 90, cex=1.25, label="Observed\nOutputs",
     pos=4, col=util$c_mid_teal)
```

We can also use the `add` argument of `plot_line_hist` to overlay multiple
histogram outlines onto an existing axis.

```{r}
plot(0, type="n",
     xlim=c(-6, 7), xlab="",
     ylim=c(0, 160), ylab="Counts")

util$plot_line_hist(data$x, -6, 6, 0.5, col="black", add=TRUE)
util$plot_line_hist(data$y, -4, 7, 0.5, col=util$c_mid_teal, add=TRUE)

text(-3.5, 90, cex=1.25, label="Observed\nInputs",
     pos=4, col="black")
text(3.5, 90, cex=1.25, label="Observed\nOutputs",
     pos=4, col=util$c_mid_teal)
```

## Prior Checks

Here we'll be exceptionally thorough and start with an investigation of the
prior model and its consequences.  In addition to the individual parameters
we'll look at the prior behavior of baseline function and the prior predictive
distribution along a grid of inputs defined by the `x_grid` array.

```{.stan include="stan_programs/uni_prior_model.stan" filename="uni\\_prior\\_model.stan" eval=FALSE}
```

Note that I'm using a less-aggressive step size adaptation here because the
half-normal prior model for $\sigma$ results in an slightly awkward tail for the
unconstrained $\log(\sigma)$ values that can be a bit difficult to navigate.

```{r}
#| warning: false
#| message: false
data$N_grid <- 1000
data$x_grid <- seq(-6, 6, 12 / (data$N_grid - 1))

fit <- stan(file='stan_programs/uni_prior_model.stan',
            data=data, seed=5838299,
            warmup=1000, iter=2024, refresh=0,
            control=list('adapt_delta' = 0.9))
```

Of course we always consult our diagnostics first to make sure that our Markov
chains, and hence any visualization we derive from them, accurately characterize
the exact target distribution, in this case the prior distribution of our model.

```{r}
diagnostics <- util$extract_hmc_diagnostics(fit)
util$check_all_hmc_diagnostics(diagnostics)

samples <- util$extract_expectand_vals(fit)
base_samples <- util$filter_expectands(samples,
                                       c('alpha', 'beta', 'sigma'))
util$check_all_expectand_diagnostics(base_samples)
```

We can visualize the probability distribution of baseline functions in two ways.
Firstly we can plot a subset of baseline function configurations.  Secondly we
can plot nested quantile intervals that quantify the marginal behavior of the
function output at each input.  Neither of these visualizations fully
characterize the probabilistic behavior but together they capture the most
important features.

The `plot_realizations` function plots a selection of values corresponding to
the `f_names` array against `data$x_grid` while the
`plot_conn_pushforward_quantiles` function plots nested quantile intervals of
those values for each element of `data$x_grid`.  Here "conn" refers to
"connected" as the individual marginal quantiles are connected into continuous
polygons.

```{r}
par(mfrow=c(2, 1))

f_names <- sapply(1:data$N_grid,
                  function(n) paste0('f_grid[', n, ']'))
util$plot_realizations(samples, f_names, data$x_grid,
                       xlab="x", ylab="f")
util$plot_conn_pushforward_quantiles(samples, f_names, data$x_grid,
                                     xlab="x", ylab="f")
```

Finally let's use the `plot_conn_pushforward_quantiles` function to plot nested
quantile intervals of the conditional prior predictive behavior at each element
of `data$x_grid`.

```{r}
par(mfrow=c(1, 1))

pred_names <- sapply(1:data$N_grid,
                     function(n) paste0('y_pred_grid[', n, ']'))
util$plot_conn_pushforward_quantiles(samples, pred_names, data$x_grid,
                                     xlab="x", ylab="y")
```

## Posterior Inference

Having thoroughly investigated our prior model and its consequences and not
found any undesired behavior we can move on to constructing posterior
inferences.

```{.stan include="stan_programs/uni_full_model.stan" filename="uni\\_full\\_model.stan" eval=FALSE}
```

```{r}
#| warning: false
#| message: false
fit <- stan(file='stan_programs/uni_full_model.stan',
            data=data, seed=5838299,
            warmup=1000, iter=2024, refresh=0)
```

There are no signs of trouble from the computational diagnostics.

```{r}
diagnostics <- util$extract_hmc_diagnostics(fit)
util$check_all_hmc_diagnostics(diagnostics)

samples <- util$extract_expectand_vals(fit)
base_samples <- util$filter_expectands(samples,
                                       c('alpha', 'beta', 'sigma'))
util$check_all_expectand_diagnostics(base_samples)
```

Before examining any posterior inferences, however, we need to validate that our
model is adequately capturing the relevant features of the observed data.  For
this one-dimensional baseline function model we can implement an informative
retrodictive check by comparing the conditional posterior predictive
distributions at each input,
$$
p(y \mid x,
         \tilde{x}_{1}, \tilde{y}_{1}, \ldots, \tilde{x}_{N}, \tilde{y}_{N}),
$$
to the observed input-output pairs, $(x_{n}, y_{n})$.

```{r}
par(mfrow=c(1, 1))

pred_names <- sapply(1:data$N_grid,
                     function(n) paste0('y_pred_grid[', n, ']'))
util$plot_conn_pushforward_quantiles(samples, pred_names, data$x_grid,
                                     xlab="x", ylab="y")
points(data$x, data$y, pch=16, cex=1.0, col="white")
points(data$x, data$y, pch=16, cex=0.8, col="black")
```

Fortunately there are no signs of tension between the posterior predictive
distributional behaviors and the observed behaviors.  Confident in the adequacy
of our model we can move onto visualizing posterior inferences.

For example we can visualize the pushforward, or marginal, probability
distributions for each parameter.  Note that the `plot_expectand_pushforward`
function is already part of my Markov chain Monte Carlo analysis tools and not
one of the visualization functions being introduced here.

```{r}
par(mfrow=c(1, 3))

util$plot_expectand_pushforward(samples[["alpha"]], 25,
                                display_name="alpha")

util$plot_expectand_pushforward(samples[["beta"]], 25,
                                display_name="beta")

util$plot_expectand_pushforward(samples[["sigma"]], 25,
                                display_name="sigma")

```

Communicating the posterior behavior of the baseline function, however, is
facilitated with the new visualization functions.

```{r}
par(mfrow=c(2, 1))

f_names <- sapply(1:data$N_grid,
                  function(n) paste0('f_grid[', n, ']'))
util$plot_realizations(samples, f_names, data$x_grid,
                       xlab="x", ylab="f")
util$plot_conn_pushforward_quantiles(samples, f_names, data$x_grid,
                                     xlab="x", ylab="f")
```

Conveniently all of these visualization functions feature optional arguments
for baseline behavior which allows us to compare our posterior inferences to
the true behavior when it is known, for example in simulation studies.

```{r}
true_alpha <- 1.5
true_beta <- -0.75
true_sigma <- 0.33

par(mfrow=c(1, 3))

util$plot_expectand_pushforward(samples[["alpha"]], 25,
                                display_name="alpha",
                                baseline=true_alpha,
                                baseline_col=util$c_mid_teal)

util$plot_expectand_pushforward(samples[["beta"]], 25,
                                display_name="beta",
                                baseline=true_beta,
                                baseline_col=util$c_mid_teal)

util$plot_expectand_pushforward(samples[["sigma"]], 25,
                                display_name="sigma",
                                baseline=true_sigma,
                                baseline_col=util$c_mid_teal)
```

```{r}
true_fs <- true_alpha + true_beta * data$x_grid

par(mfrow=c(2, 1))

util$plot_realizations(samples, f_names, data$x_grid,
                       baseline_values=true_fs,
                       baseline_col=util$c_mid_teal,
                       xlab="x", ylab="f")
util$plot_conn_pushforward_quantiles(samples, f_names, data$x_grid,
                                     baseline_values=true_fs,
                                     baseline_col=util$c_mid_teal,
                                     xlab="x", ylab="f")
```

The `plot_realizations` and `plot_conn_pushforward_quantiles` functions also
include `residual` arguments that allow us to directly visualize how the
probabilistic behavior varies around the baseline values.

```{r}
par(mfrow=c(2, 1))

util$plot_realizations(samples, f_names, data$x_grid,
                       baseline_values=true_fs,
                       residual=TRUE,
                       xlab="x", ylab="f")
util$plot_conn_pushforward_quantiles(samples, f_names, data$x_grid,
                                     baseline_values=true_fs,
                                     residual=TRUE,
                                     xlab="x", ylab="f")
```

# Multi-Dimensional Baseline Function

Now that we're warmed up let's consider a three-dimensional curve-fitting model
with a quadratic baseline function,
$$
p(y_{n} \mid \mathbf{x}_{n}, \alpha, \beta, \sigma)
=
\text{normal}(y_{n}   \mid \beta_{0}
                    + \boldsymbol{\beta}^{T} \cdot \mathbf{x}
                    + \mathbf{x}^{T} \cdot \mathbf{B} \cdot \mathbf{x}, \sigma),
$$
where $\mathbf{B}$ is a positive-definite matrix whose three diagonal elements
are organized into the vector $\boldsymbol{\beta}_{d}$ and three off-diagonal
elements are organized into the vector $\boldsymbol{\beta}_{o}$.

## Plot Data

The `plot_line_hist` allows us to cleanly visualize each component of the
observed inputs.

```{r}
data <- read_rdump("data/multi_data.R")

par(mfrow=c(3, 3), mar = c(5, 5, 2, 1))

util$plot_line_hist(data$X[,1], -9, 9, 1, xlab="x1")
util$plot_line_hist(data$X[,2], -9, 9, 1, xlab="x1")
util$plot_line_hist(data$X[,3], -9, 9, 1, xlab="x1")

plot(data$X[,1], data$X[,2], pch=16, cex=1.0, col="black",
     main="", xlim=c(-9, 9), xlab="x1", ylim=c(-9, 9), ylab="x2")

plot(data$X[,1], data$X[,3], pch=16, cex=1.0, col="black",
     main="", xlim=c(-9, 9), xlab="x1", ylim=c(-9, 9), ylab="x3")

plot(data$X[,2], data$X[,3], pch=16, cex=1.0, col="black",
     main="", xlim=c(-9, 9), xlab="x2", ylim=c(-9, 9), ylab="x3")

plot(data$X[,1], data$y, pch=16, cex=1.0, col="black",
     main="", xlim=c(-9, 9), xlab="x1", ylim=c(-25, 325), ylab="y")

plot(data$X[,2], data$y, pch=16, cex=1.0, col="black",
     main="", xlim=c(-9, 9), xlab="x2", ylim=c(-25, 325), ylab="y")

plot(data$X[,3], data$y, pch=16, cex=1.0, col="black",
     main="", xlim=c(-9, 9), xlab="x3", ylim=c(-25, 325), ylab="y")
```

## Prior Checks

As before we'll first investigate the consequences of our prior model.

For a discussion of why the quadratic baseline model is implemented in this way
see Section 2.3.2 of my
[Taylor regression modeling chapter](https://betanalpha.github.io/assets/case_studies/taylor_models.html#232_Higher-Order_Implementations).

```{.stan include="stan_programs/multi_prior_model.stan" filename="multi\\_prior\\_model.stan" eval=FALSE}
```

```{r}
#| warning: false
#| message: false
fit <- stan(file='stan_programs/multi_prior_model.stan',
            data=data, seed=5838299,
            warmup=1000, iter=2024, refresh=0)
```

Higher-dimensional probability distributions are no trouble for Hamiltonian
Monte Carlo.

```{r}
diagnostics <- util$extract_hmc_diagnostics(fit)
util$check_all_hmc_diagnostics(diagnostics)

samples <- util$extract_expectand_vals(fit)
base_samples <- util$filter_expectands(samples,
                                       c('beta0', 'beta1',
                                         'beta2_d', 'beta2_o',
                                         'sigma'),
                                       TRUE)
util$check_all_expectand_diagnostics(base_samples)
```

With a multi-dimensional input space we can no longer visualize the baseline
functional behavior nor the conditional prior predictive behavior directly.
We can, however, visualize many of its features.

For example we might consider the marginal behavior of the predicted outputs,
regardless of the corresponding observed inputs.  Here we'll summarize this
marginal behavior with a histogram, and use the `plot_hist_quantiles` function
to visualize the prior predictive distribution of the histogram counts.

```{r}
par(mfrow=c(1, 1))

util$plot_hist_quantiles(samples, 'y_pred')
```

We can also set the binning by hand, either with bounds a fixed bin width
or an arbitrary bin configuration.

```{r}
par(mfrow=c(1, 1))

util$plot_hist_quantiles(samples, 'y_pred', -400, 400, 50)
```

```{r}
par(mfrow=c(1, 1))

util$plot_hist_quantiles(samples, 'y_pred',
                         breaks=c(-400, -200, -100, -50, -25, 0,
                                  25, 50, 100, 200, 400))
```

To capture the interactions between the predictive outputs and the observed
input components we'll need a more sophisticated summary statistic.  Here we'll
use the empirical mean and medians of the predictive outputs within bins of each
input component.  For a detailed discussion of how this summary statistic is
constructed see Section 2.5 of my
[Taylor regression modeling chapter](https://betanalpha.github.io/assets/case_studies/taylor_models.html#25_Posterior_Retrodictive_Checks).

Conveniently the `plot_conditional_mean_quantiles` and
`plot_conditional_median_quantiles` functions visualize the prior predictive
behavior of these summary statistics.

```{r}
par(mfrow=c(1, 3))

pred_names <- sapply(1:data$N, function(n) paste0('y_pred[', n, ']'))
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,1],
                                     -9, 9, 1, xlab="x1")
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,2],
                                     -9, 9, 1,xlab="x2")
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,3],
                                     -9, 9, 1, xlab="x3")
```

```{r}
par(mfrow=c(1, 3))

pred_names <- sapply(1:data$N, function(n) paste0('y_pred[', n, ']'))
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,1],
                                       -9, 9, 1, xlab="x1")
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,2],
                                       -9, 9, 1, xlab="x2")
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,3],
                                       -9, 9, 1, xlab="x3")
```

## Posterior Inference

Now we're ready to incorporate the observed data.

```{.stan include="stan_programs/multi_full_model.stan" filename="multi\\_full\\_model.stan" eval=FALSE}
```

```{r}
#| warning: false
#| message: false
fit <- stan(file='stan_programs/multi_full_model.stan',
            data=data, seed=5838299,
            warmup=1000, iter=2024, refresh=0)
```

Fortunately our computational fortune has persisted.

```{r}
diagnostics <- util$extract_hmc_diagnostics(fit)
util$check_all_hmc_diagnostics(diagnostics)

samples <- util$extract_expectand_vals(fit)
base_samples <- util$filter_expectands(samples,
                                       c('beta0', 'beta1',
                                         'beta2_d', 'beta2_o',
                                         'sigma'),
                                       TRUE)
util$check_all_expectand_diagnostics(base_samples)
```

The summary statistics that we used above to implement our prior predictive
checks are equally useful for implementing informative posterior retrodictive
checks.  Conveniently the visualization functions all feature `baseline_values`
functions that we can use to visualize the observed behavior along with the
posterior predictive behavior.

```{r}
par(mfrow=c(1, 1))

util$plot_hist_quantiles(samples, 'y_pred', baseline_values=data$y)
```

Additionally the `plot_conditional_mean_quantiles` and
`plot_conditional_median_quantiles` functions feature a `residual` option that
plots the posterior predictive behaviors relative to the baseline values.  Any
deviations from zero in these plots suggests retrodictive tension; here,
however, there don't seem to be any problems.

```{r}
par(mfrow=c(2, 3))

pred_names <- sapply(1:data$N, function(n) paste0('y_pred[', n, ']'))
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,1],
                                     -9, 9, 1, data$y, xlab="x1")
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,2],
                                     -9, 9, 1, data$y, xlab="x2")
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,3],
                                     -9, 9, 1, data$y, xlab="x3")
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,1],
                                     -9, 9, 1, data$y, residual=TRUE,
                                     xlab="x1")
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,2],
                                     -9, 9, 1, data$y, residual=TRUE,
                                     xlab="x2")
util$plot_conditional_mean_quantiles(samples, pred_names, data$X[,3],
                                     -9, 9, 1, data$y, residual=TRUE,
                                     xlab="x3")
```

```{r}
par(mfrow=c(2, 3))

pred_names <- sapply(1:data$N, function(n) paste0('y_pred[', n, ']'))
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,1],
                                       -9, 9, 1, data$y, xlab="x1")
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,2],
                                       -9, 9, 1, data$y, xlab="x2")
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,3],
                                       -9, 9, 1, data$y, xlab="x3")
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,1],
                                       -9, 9, 1, data$y, residual=TRUE,
                                       xlab="x1")
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,2],
                                       -9, 9, 1, data$y, residual=TRUE,
                                       xlab="x2")
util$plot_conditional_median_quantiles(samples, pred_names, data$X[,3],
                                       -9, 9, 1, data$y, residual=TRUE,
                                       xlab="x3")
```

With no indications of model inadequacy we can move onto our posterior
inferences.  As before we can visualize the pushforward posterior distributions
for each individual, one-dimensional parameter.

```{r}
par(mfrow=c(4, 3))

util$plot_expectand_pushforward(samples[["beta0"]], 25,
                                display_name="beta0")

plot.new()

util$plot_expectand_pushforward(samples[["sigma"]], 25,
                                display_name="sigma")

for (m in 1:data$M) {
  name <- paste0('beta1[', m, ']')
  util$plot_expectand_pushforward(samples[[name]], 25,
                                  display_name=name)
}

for (m in 1:data$M) {
  name <- paste0('beta2_d[', m, ']')
  util$plot_expectand_pushforward(samples[[name]], 25,
                                  display_name=name)
}

for (m in 1:data$M) {
  name <- paste0('beta2_o[', m, ']')
  util$plot_expectand_pushforward(samples[[name]], 25,
                                  display_name=name)
}
```

The `plot_disc_pushforward_quantiles` function plots disconnected, marginal
nested quantile intervals for a collection of one-dimensional variables.  This
allows for a more compact visualization of the marginal posterior distributions.

```{r}
par(mfrow=c(1, 3))

names <- sapply(1:data$M, function(m) paste0('beta1[', m, ']'))
util$plot_disc_pushforward_quantiles(samples, names,
                                     xlab="beta1",
                                     ylab="Marginal Posterior Quantiles")

names <- sapply(1:data$M, function(m) paste0('beta2_d[', m, ']'))
util$plot_disc_pushforward_quantiles(samples, names,
                                     xlab="beta2_d",
                                     ylab="Marginal Posterior Quantiles")

names <- sapply(1:data$M, function(m) paste0('beta2_o[', m, ']'))
util$plot_disc_pushforward_quantiles(samples, names,
                                     xlab="beta2_o",
                                     ylab="Marginal Posterior Quantiles")
```

```{r}
par(mfrow=c(1, 1))

names <- c(sapply(1:data$M, function(m) paste0('beta1[', m, ']')),
           sapply(1:data$M, function(m) paste0('beta2_d[', m, ']')),
           sapply(1:data$M, function(m) paste0('beta2_o[', m, ']')))
util$plot_disc_pushforward_quantiles(samples, names,
                                     xlab="All Slopes",
                                     ylab="Marginal Posterior Quantiles")
```

This function also includes an optional `baseline_values` argument and
`residual` configuration which we can use to compare the probabilistic to the
point values, for example our marginal posterior inferences to the true values
when analyzing simulated data.

```{r}
true_slopes <- c(-6.00, -1.50, 13.00,  0.50, 0.25,
                 1.00, -0.50, -2.00, -1.00)

par(mfrow=c(2, 1))

util$plot_disc_pushforward_quantiles(samples, names,
                                     baseline_values=true_slopes,
                                     baseline_col=util$c_mid_teal,
                                     xlab="All Slopes",
                                     ylab="Marginal Posterior\nQuantiles")

util$plot_disc_pushforward_quantiles(samples, names,
                                     baseline_values=true_slopes,
                                     residual=TRUE,
                                     xlab="All Slopes",
                                     ylab="Marginal Posterior\nQuantile Residuals")
```

# License {-}

The code in this case study is copyrighted by Michael Betancourt and licensed
under the new BSD (3-clause) license:

https://opensource.org/licenses/BSD-3-Clause

The text and figures in this case study are copyrighted by Michael Betancourt
and licensed under the CC BY-NC 4.0 license:

https://creativecommons.org/licenses/by-nc/4.0/

# Original Computing Environment {-}

```{r, comment=NA}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))
```

```{r, comment=NA}
sessionInfo()
```
